```
# Liisbeth's code for LPS study behavioral analysis

##### Edited by Holland Brown to plot effect of block (time) on behav scores

##### Updated 2024-12-03
##### Created 2024-09-09

## Notes:
#### Get timing info (block labels) from /LPS_STHLM/sourcedata/InteroceptionLogFiles/ses-0{1-4}_onsets.csv
#### BQ = body question (i.e. interoception); WQ = word question (i.e. exteroception)

```

#1. Packages
```{r}
library(dplyr)         #needed for filtering the data
library(ggplot2)       #needed for plotting the data
library(reshape2)      #needed for changing between long/wide format
library(readxl)        #needed for importing excel files
library(ggpubr)        #needed for adding significance bars to plots
library(car)           #for recoding the values

# Mixed effects linear models
library(lme4)
library(lmerTest)
library(emmeans) # post-hoc comparisons

# Other useful R packages
library(glue) # lets me code sort of like I can with f-strings in Python (sort of)
library(rlang) # need this for the := operator
```

#2. Setting the working directory and importing behavioral data
```{r}
setwd("/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data") # location of data and this script
task_ses1 <- read.csv("summary_ses-01_interoception_responses.csv") # contains condition, reaction time, and response for one session
task_all_sessions <- read.csv("summary_allsessions_interoception_responses.csv") # contains condition, reaction time, and response for all sessions
task_all_sessions_acc <- read.csv("summary_allsessions_interoception_acc.csv") # contains condition, reaction time, response, and accuracy for all sessions
session_conditions <- read_excel("cond_ses_info.xlsx") # contains condition names ("morningpl", "morninglps", etc)
```

#3. Data preparation
```{r}

## 3.1. Merging the info from two datasets: Matching session number (e.g. "ses-01") to the condition (e.g. "plmorning")
session_long <- melt(session_conditions, id.vars = c("subjectID", "anat", "pls", "group"), value.name = "session_cond", variable.name = "session_num") # change session info file to long format

# Merge task_all_sessions, task_all_sessions_acc by matching subject ID, condition, reaction time, session, and response
merged_all_sessions_acc <- left_join(task_all_sessions, task_all_sessions_acc, by=join_by(subjid == subjid, cond == cond, rt == rt, session == session, resp == resp), relationship = "many-to-one", multiple = "first")

# Merge the datasets based on matching subject IDs and session numbers in both datasets. Result is a merged dataset containing the session number and session condition
merged_all_sessions <- left_join(merged_all_sessions_acc, session_long, by=join_by(subjid == subjectID, session == session_num))

## 3.2. Recoding the labels (recode responses on the 4-point scale in the opposite direction)
merged_all_sessions$resp_re <- car::recode(merged_all_sessions$resp, "1 = 4; 2 = 3; 3 = 2; 4 = 1")
merged_all_sessions$cresp_re <- car::recode(merged_all_sessions$cresp, "1 = 4; 2 = 3; 3 = 2; 4 = 1")

## 3.3. Separating interoception and exteroception
### 3.3.1. Interoception: Separating BQ1 & BQ2
merged_inter <- data.frame(dplyr::filter(merged_all_sessions, merged_all_sessions$cond == "BQ1" | merged_all_sessions$cond == "BQ2"))
merged_interBQ1 <- data.frame(dplyr::filter(merged_all_sessions, merged_all_sessions$cond == "BQ1"))
merged_interBQ2 <- data.frame(dplyr::filter(merged_all_sessions, merged_all_sessions$cond == "BQ2"))

####### Filtering for participants, who have data for all sessions
complete_BQ1 <- dplyr::filter(merged_interBQ1, merged_interBQ1$subjid != "sub-120" & merged_interBQ1$subjid != "sub-138" & merged_interBQ1$subjid != "sub-141")
complete_BQ2 <- dplyr::filter(merged_interBQ2, merged_interBQ1$subjid != "sub-120" & merged_interBQ1$subjid != "sub-138" & merged_interBQ1$subjid != "sub-141")

### 3.3.1. Exteroception: Separating WQ1 & WQ2
merged_exte <- data.frame(dplyr::filter(merged_all_sessions, merged_all_sessions$cond == "WQ1" | merged_all_sessions$cond == "WQ2"))
merged_exteWQ1 <- data.frame(dplyr::filter(merged_all_sessions, merged_all_sessions$cond == "WQ1"))
merged_exteWQ2 <- data.frame(dplyr::filter(merged_all_sessions, merged_all_sessions$cond == "WQ2"))

####### Filtering for participants, who have data for all sessions
complete_WQ1 <- dplyr::filter(merged_exteWQ1, merged_exteWQ1$subjid != "sub-120" & merged_exteWQ1$subjid != "sub-138" & merged_exteWQ1$subjid != "sub-141")
complete_WQ2 <- dplyr::filter(merged_exteWQ2, merged_exteWQ1$subjid != "sub-120" & merged_exteWQ1$subjid != "sub-138" & merged_exteWQ1$subjid != "sub-141")


```


#4. Mixed effects linear models

##4.1 Linear models: one question, one session at a time
```{r}
# PURPOSE: these models can't be compared to one another bc random intercepts used to compensate for random effect will differ between models, however, it will show us if for some questions or sessions the effects are statistically significant

savedir <- "/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/plots_change_over_block/20241213_one_question_one_session_lmer"

# Step 1: Fit Mixed-Effects Model (use from prev code block)
#df1 <- merged_exteWQ2 # exteroception questions
df1 <- merged_interBQ2 # interoception questions

df_lps <- data.frame(dplyr::filter(df1, df1$session_cond == "lps")) # extract one session from df with one question
df_lpsmorning <- data.frame(dplyr::filter(df1, df1$session_cond == "lpsmorning")) # extract one session from df with one question
df_pl <- data.frame(dplyr::filter(df1, df1$session_cond == "pl")) # extract one session from df with one question
df_plmorning <- data.frame(dplyr::filter(df1, df1$session_cond == "plmorning")) # extract one session from df with one question
```
```{r}
# Fit the model
df <- df_plmorning # run one session at a time
model <- lmer(resp ~ block + (1 | subjid), data = df)

# Summary stats of the model
summary(model)
fixef(model) # Full table of fixed effects
coef(summary(model)) # Full table of coefficients
anova(model) # Full table from ANOVA test

# Step 2: Generate Predictions ---------------------------------------------------
# Create a new data frame for predictions over trials and conditions
pred_data <- expand.grid(
  block = 1:10,
  session_cond = unique(df$session_cond)
)

# Add predictions from the model
pred_data$pred <- predict(model, newdata = pred_data, re.form = NA)  # re.form = NA excludes random effects

# Step 3: Summarize Reaction Time Data -------------------------------------------
summary <- df %>%
  group_by(session_cond, block) %>%
  summarise(
    mean = mean(acc, na.rm = TRUE),
    se = sd(acc, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci = mean - 1.96 * se,      # Lower bound of 95% CI
    upper_ci = mean + 1.96 * se) %>%       # Upper bound of 95% CI
  ungroup()

```

##4.1 Effect of block on reaction time, response, and accuracy with condtion, time of day, and (condition * time) as fixed effects, subject as a random effect
```{r}
# Predicted reaction times for all sessions, 1 question at a time

# Step 1: Fit Mixed-Effects Model (use from prev code block)
# afternoon <- data.frame(dplyr::filter(merged_all_sessions, merged_all_sessions$session_cond == "lps" | merged_all_sessions$session_cond == "pl"))
# morning <- data.frame(dplyr::filter(merged_all_sessions, merged_all_sessions$session_cond == "lpsmorning" | merged_all_sessions$session_cond == "plmorning"))
df <- merged_exteWQ1
new_column_name1 <- "time_of_day"  # Dynamically define the new column name

# Add column for time of day (morning or afternoon)
df_lmer <- df %>%
  mutate(
    !!new_column_name1 := case_when(
      session_cond == "plmorning" | session_cond == "lpsmorning" ~ "morning",
      session_cond == "pl" | session_cond == "lps" ~ "afternoon",
      TRUE ~ "Other"  # Default case (optional, in case other values exist)
    )
  )

# Add column for condition (lps or placebo)
new_column_name2 <- "condition"  # Dynamically define the new column name

df_lmer <- df_lmer %>%
  mutate(
    !!new_column_name2 := case_when(
      session_cond == "plmorning" | session_cond == "pl" ~ "pl",
      session_cond == "lpsmorning" | session_cond == "lps" ~ "lps",
      TRUE ~ "Other"  # Default case (optional, in case other values exist)
    )
  )

# df <- df$new_col <- ifelse(df$col1 > 5, "morning", "afternoon")  # interoception questions
```


```{r}

# Set one condition to be the reference level for the LMER (choose 'plmorning')
df_lmer$session_cond <- factor(df_lmer$session_cond)
df_lmer$session_cond <- relevel(df_lmer$session_cond, ref = "plmorning")


# Fit the model
model <- lmer(acc ~ block * session_cond * time_of_day * (session_cond * time_of_day) + (1 | subjid), data = df_lmer)

# Summary stats of the model
summary(model)
fixef(model) # Full table of fixed effects
coef(summary(model)) # Full table of coefficients
anova(model) # Full table from ANOVA test

# Step 2: Generate Predictions ---------------------------------------------------
# Create a new data frame for predictions over trials and conditions
pred_data <- expand.grid(
  block = 1:10,
  condition = unique(df_lmer$session_cond),
  time_of_day = unique(df_lmer$time_of_day),
  subjid = unique(df_lmer$subjid),
  session_cond = unique(df_lmer$session_cond)
)

# Add predictions from the model
pred_data$pred_rt <- predict(model, newdata = pred_data, re.form = NA)  # re.form = NA excludes random effects

# Step 3: Summarize Reaction Time Data -------------------------------------------
summary_rt <- df_lmer %>%
  group_by(session_cond, block) %>%
  summarise(
    mean_rt = mean(acc, na.rm = TRUE),
    se_rt = sd(acc, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_rt = mean_rt - 1.96 * se_rt,      # Lower bound of 95% CI
    upper_ci_rt = mean_rt + 1.96 * se_rt) %>%       # Upper bound of 95% CI
  ungroup()

# Step 4: Plot Reaction Time with Model Predictions -----------------------------
# plot_title_rt <- "WQ1 Predicted Reaction Time Over Trials"
# # color_ord <- list("lps","lpsmorning","pl","plmorning") # define order of condition variables so color palettes match other plots
# 
# ggplot(pred_data, aes(x = block, y = pred_rt, color = session_cond, group = session_cond)) +
#   
#   # Plot the line for predicted values
#   geom_line(size = 1.2) +
#   
#   # Add points for each trial to highlight individual predicted values
#   geom_point(size = 2) +
#   
#   # Labels and theme adjustments
#   labs(title = plot_title_rt,
#        x = "Trials",
#        y = "Predicted Reaction Time (sec)") +
#   
#   # Customize x-axis for trial numbers
#   scale_x_continuous(breaks = 1:10) +
#   
#   theme_minimal() +
#   theme(legend.position = "right")  # Show legend if useful

# Save the predicted response plot
#ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/plots_change_over_block/BQ2_predicted_rt.png', bg = 'white')
```

##4.2 Effect of block on reaction time, response, and accuracy with subject as a random effect (one session at a time)
```{r}
# Effect of block on reaction time, response, and accuracy with subject as a random effect (one session at a time)

# Step 1: Fit Mixed-Effects Model (use from prev code block)
df <- data.frame(dplyr::filter(merged_interBQ2, merged_interBQ2$session_cond == "lps")) # extract one session from df with one question
# df <- merged_exte # exteroception questions
# df <- merged_interBQ2 # interoception questions

# Fit the model
model <- lmer(rt ~ block + (1 | subjid), data = df)

# Summary stats of the model
summary(model)
fixef(model) # Full table of fixed effects
coef(summary(model)) # Full table of coefficients
anova(model) # Full table from ANOVA test

# Step 2: Generate Predictions ---------------------------------------------------
# Create a new data frame for predictions over trials and conditions
pred_data <- expand.grid(
  block = 1:10,
  session_cond = unique(df$session_cond)
)

# Add predictions from the model
pred_data$pred_rt <- predict(model, newdata = pred_data, re.form = NA)  # re.form = NA excludes random effects

# Step 3: Summarize Reaction Time Data -------------------------------------------
summary_rt <- df %>%
  group_by(session_cond, block) %>%
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    se_rt = sd(rt, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_rt = mean_rt - 1.96 * se_rt,      # Lower bound of 95% CI
    upper_ci_rt = mean_rt + 1.96 * se_rt) %>%       # Upper bound of 95% CI
  ungroup()

# Step 4: Plot Reaction Time with Model Predictions -----------------------------
plot_title_rt <- "LPS: BQ2 Predicted Reaction Time Over Trials"
# color_ord <- list("lps","lpsmorning","pl","plmorning") # define order of session_cond variables so color palettes match other plots

ggplot(pred_data, aes(x = block, y = pred_rt, color = session_cond, group = session_cond)) +
  
  # Plot the line for predicted values
  geom_line(size = 1.2) +
  
  # Add points for each trial to highlight individual predicted values
  geom_point(size = 2) +
  
  # Labels and theme adjustments
  labs(title = plot_title_rt,
       x = "Trials",
       y = "Predicted Reaction Time (sec)") +
  
  # Customize x-axis for trial numbers
  scale_x_continuous(breaks = 1:10) +
  
  theme_minimal() +
  theme(legend.position = "right")  # Show legend if useful

# Save the predicted response plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/plots_change_over_block/lps_BQ2_predicted_rt.png', bg = 'white')
```

```{r}
# Predicted accuracy for all sessions, 1 question at a time (WQ1 only)

# Step 1: Fit Mixed-Effects Model (use from prev code block)
# df <- merged_exte # exteroception questions
df <- merged_exteWQ1 # interoception questions

# Fit the model
model <- lmer(acc ~ block * session_cond + (1 | subjid), data = df)

# Summary stats of the model
summary(model)
fixef(model) # Full table of fixed effects
coef(summary(model)) # Full table of coefficients
anova(model) # Full table from ANOVA test

# Step 2: Generate Predictions ---------------------------------------------------
# Create a new data frame for predictions over trials and conditions
pred_data <- expand.grid(
  block = 1:10,
  session_cond = unique(df$session_cond)
)

# Add predictions from the model
pred_data$pred_acc <- predict(model, newdata = pred_data, re.form = NA)  # re.form = NA excludes random effects

# Step 3: Summarize Reaction Time Data -------------------------------------------
summary_resp <- df %>%
  group_by(session_cond, block) %>%
  summarise(
    mean_resp = mean(acc, na.rm = TRUE),
    se_resp = sd(acc, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_resp = mean_resp - 1.96 * se_resp,      # Lower bound of 95% CI
    upper_ci_resp = mean_resp + 1.96 * se_resp) %>%       # Upper bound of 95% CI
  ungroup()

# Step 4: Plot Reaction Time with Model Predictions -----------------------------
plot_title_resp <- "WQ1 Predicted Accuracy Over Trials"

ggplot(pred_data, aes(x = block, y = pred_acc, color = session_cond, group = session_cond)) +
  
  # Plot the line for predicted values
  geom_line(size = 1.2) +
  
  # Add points for each trial to highlight individual predicted values
  geom_point(size = 2) +
  
  # Labels and theme adjustments
  labs(title = plot_title_resp,
       x = "Trials",
       y = "Predicted Accuracy (0 for incorrect, 1 for correct)") +
  
  # Customize x-axis for trial numbers
  scale_x_continuous(breaks = 1:10) +
  
  theme_minimal() +
  theme(legend.position = "right")  # Show legend if useful

# Save the predicted response plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/plots_change_over_block/WQ1_predicted_acc.png', bg = 'white')
```

```{r}
# Predicted responses for all sessions, 1 question at a time (WQ2, BQ1, BQ2)

# Step 1: Fit Mixed-Effects Model (use from prev code block)
# df <- merged_exte # exteroception questions
df <- merged_interBQ2 # interoception questions

# Fit the model
model <- lmer(resp ~ block * session_cond + (1 | subjid), data = df)

# Summary stats of the model
summary(model)
fixef(model) # Full table of fixed effects
coef(summary(model)) # Full table of coefficients
anova(model) # Full table from ANOVA test

# Step 2: Generate Predictions ---------------------------------------------------
# Create a new data frame for predictions over trials and conditions
pred_data <- expand.grid(
  block = 1:10,
  session_cond = unique(df$session_cond)
)

# Add predictions from the model
pred_data$pred_resp <- predict(model, newdata = pred_data, re.form = NA)  # re.form = NA excludes random effects

# Step 3: Summarize Reaction Time Data -------------------------------------------
summary_resp <- df %>%
  group_by(session_cond, block) %>%
  summarise(
    mean_resp = mean(resp, na.rm = TRUE),
    se_resp = sd(resp, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_resp = mean_resp - 1.96 * se_resp,      # Lower bound of 95% CI
    upper_ci_resp = mean_resp + 1.96 * se_resp) %>%       # Upper bound of 95% CI
  ungroup()

# Step 4: Plot Reaction Time with Model Predictions -----------------------------
plot_title_resp <- "BQ2 Predicted Responses Over Trials"

ggplot(pred_data, aes(x = block, y = pred_resp, color = session_cond, group = session_cond)) +
  
  # Plot the line for predicted values
  geom_line(size = 1.2) +
  
  # Add points for each trial to highlight individual predicted values
  geom_point(size = 2) +
  
  # Labels and theme adjustments
  labs(title = plot_title_resp,
       x = "Trials",
       y = "Predicted Responses (range 1 to 4, higher value == felt more)") +
  
  # Customize x-axis for trial numbers
  scale_x_continuous(breaks = 1:10) +
  
  theme_minimal() +
  theme(legend.position = "right")  # Show legend if useful

# Save the predicted response plot
# ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/plots_change_over_block/WQ2_predicted_resp.png', bg = 'white')
```


##4.2 Effect of block on reaction time with condition as a fixed effect and subject as a random effect
```{r}
# df <- merged_exte # exteroception
df <- merged_inter # interoception

# Fit the model
model <- lmer(rt ~ block * session_cond + (1 | subjid), data = df)

# Summary of the model
summary(model)

# Check residuals
# plot(model)

# Perform ANOVA to check significance of terms
anova(model)

# Post-hoc comparisons
emmeans(model, pairwise ~ block * session_cond)

```


##4.5 Difference in block effects across conditions and extero/intero
```{r}
df <- merged_all_sessions # interoception and exteroception

# Modify the model to focus on block and condition interaction
model_block_condition <- lmer(rt ~ block * session_cond + (1 | subjid), data = df)

# # Summary of the model
# summary(model_block_condition)

# # Post-hoc comparisons: contrast block effects across conditions
# emm <- emmeans(model_block_condition, ~ block | session_cond, pbkrtest.limit = 3843)
# 
# # Pairwise comparison of block effects across conditions
# pairs(emm)

# run ANOVA on model to see significance of the residuals
anova(model_block_condition)

# Plot block effects across conditions
ggplot(df, aes(x = block, y = rt, color = session_cond)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ session_cond) +
  theme_minimal() +
  labs(title = "Effect of Block on Accuracy Across Conditions",
       x = "Block",
       y = "Accuracy")



```



##4.6 Difference in block effects in conditions separately
```{r}
# NOTE: in prev. model, found that block effect depends on condition, so modeling them here separately

# Conditions (session_cond)
# condition <- 'lps'
# condition <- 'pl'
# condition <- 'lpsmorning'
condition <- 'plmorning'

df_allconds <- merged_all_sessions # interoception and exteroception
df <- data.frame(dplyr::filter(df_allconds, df_allconds$session_cond == condition))

# Modify the model to focus on block and condition interaction
model <- lmer(rt ~ block + (1 | subjid), data = df)

# Summary of the model
summary(model_block_condition)

# # Post-hoc comparisons: contrast block effects across conditions
# emm <- emmeans(model_block_condition, ~ block | session_cond, pbkrtest.limit = 3843)
# 
# # Pairwise comparison of block effects across conditions
# pairs(emm)

# run ANOVA on model to see significance of the residuals
anova(model)

```

##4.6 Effect of condition on rt/resp/acc, etc. with block and subjectID as mixed effects
# NOTE: cond == BQ1, BQ2, WQ1, or WQ2 (interoception questions or exteroception questions)
```{r}
# NOTE: in prev. model, found that block effect depends on condition, so modeling them here separately

# Conditions (session_cond)
condition <- 'lps'
# condition <- 'pl'
# condition <- 'lpsmorning'
# condition <- 'plmorning'

question <- 'BQ1'

df_allconds <- merged_all_sessions_acc # interoception and exteroception
df1 <- data.frame(dplyr::filter(df_allconds, df_allconds$session_cond == condition))
df

# Modify the model to focus on block and condition interaction
model <- lmer(resp ~ cond * block + (1 | subjid), data = df)

# Summary of the model
summary(model)

# Full table of fixed effects
fixef(model)

# Full table of coefficients
coef(summary(model))

# Full table from ANOVA test
anova(model)

```


#4.6.1 Plot subjects' trajectories over time for all conditions
```
Measures to Plot:
  - reaction time (rt)
  - accuracy (acc)
  - response (resp)
  
Don't Plot
  - response reverse-coded (resp_re)
  - correct response reverse-coded (cresp_re)
  
NOTES:
  - BQ1: How strong did you feel your body?
  - BQ2: How difficult was it to focus on your body?
  - WQ1: How many times was the word mirrored? >> only question to which accuracy applies
  - WQ2: How difficult was it to count the times the word was mirrored?


  
```
```{r}
merged_BQ2_WQ2 <- rbind(complete_BQ2, complete_WQ2) # merge and save


df <- merged_BQ2_WQ2 # this will be overwritten if you rerun this for different questions
# measure <- resp # measure you want to plot (resp, cresp, rt, acc)
m_string <- "Response (Higher = more difficult)" # string describing the measure for plot titles and labels

plot_title <- glue('Task (Intero- and Exteroception) Difficulty Over Blocks')

# # Create a plot with each subject's trajectory across blocks, faceted by condition
# ggplot(df, aes(x = block, y = rt, group = subjid, color = subjid)) +
#   geom_line() +  # plot a line for each subject
#   geom_point() +  # add points at each block for each subject
#   facet_wrap(~ session_cond) +  # create a separate panel for each condition
#   theme_minimal() +  # use a minimal theme
#   labs(title = "Subject Accuracy Over Blocks Across Conditions",
#        x = "Block",
#        y = "Accuracy") +
#   theme(legend.position = "none")  # hide legend

# Calculate average measure for each block and condition
# TRY PLOTTING STDD -> see if ppl's perception of difficulty changes in a pattern
avg_data <- df %>%
  group_by(session_cond, block) %>%
  summarise(avg = sd(resp, na.rm=TRUE)) # add param to ignore NaNs
  # summarise(avg = mean(resp, na.rm=TRUE)) # add param to ignore NaNs

# Plot subject trajectories and average lines
ggplot() +
  # Plot individual subject trajectories with transparency
  geom_line(data = df, aes(x = block, y = resp, group = subjid, 
            color = subjid), alpha = 0.3) +  # make subject lines more transparent (modulate alpha)
  
  # Plot points for subject data (may remove later)
  geom_point(data = df, aes(x = block, y = resp, group = subjid,
             color = subjid), alpha = 0.3) +   # make subject points more transparent
  
  # Plot average trajectory for each condition in black
  geom_line(data = avg_data, aes(x = block, y = avg), color = "black", size = .75) +  # black average line
  geom_point(data = avg_data, aes(x = block, y = avg), color = "black", size = 1) +  # points on average line
  
  # Facet by condition (in R, a 'facet' is a figure panel)
  facet_wrap(~ session_cond) +
  
  # Labels and theme
  theme_minimal() +
  labs(title = plot_title,
       x = "Block",
       y = m_string) +
  theme(legend.position = "none")  # No legend for subjects

ggsave <- function(..., bg = 'white') ggplot2::ggsave(..., bg = bg)
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/BQ2_WQ2_resp_change_sd.png')

```

# (BQ2 and WQ2) Combined Intero- and Exteroception Difficulty Scores
```{r}
# Mean Bars
# Error Bars: mean ± 1.96 * (SE)

# Merge datasets
merged_BQ2_WQ2 <- rbind(complete_BQ2, complete_WQ2)

# Assign merged data to df
df <- merged_BQ2_WQ2
m_string <- "Response (Higher = more difficult)"  # String for plot labels

# Title for the plot
plot_title <- glue('Task (Intero- and Exteroception) Difficulty Over Blocks')

# Summarize data to calculate median, SE, and 95% confidence intervals
summary_data <- df %>%
  group_by(session_cond, block) %>%
  summarise(
    mean_resp = mean(resp, na.rm = TRUE),
    se_resp = sd(resp, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci = mean_resp - 1.96 * se_resp,       # Lower bound of 95% CI
    upper_ci = mean_resp + 1.96 * se_resp        # Upper bound of 95% CI
  )

# Create a bar plot with error bars for 95% confidence intervals
ggplot(summary_data, aes(x = factor(block), y = mean_resp, fill = session_cond)) +
  # Plot bars representing medians
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, position = position_dodge(0.9)) +
  
  # Facet by condition
  facet_wrap(~ session_cond) +
  
  # Labels and theme
  labs(title = plot_title,
       x = "Block",
       y = m_string) +
  theme_minimal() +
  theme(legend.position = "none")  # No legend for blocks

# Save the plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/BQ2_WQ2_resp_bar_mean_CI.png', bg = 'white')


```

# (WQ1) Accuracy and Reaction Time: "How many times was the word mirrored?"
```{r}
# WQ1 Reaction-times plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_rt <- complete_WQ1 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_rt <- df_rt %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    se_rt = sd(rt, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_rt = mean_rt - 1.96 * se_rt,      # Lower bound of 95% CI
    upper_ci_rt = mean_rt + 1.96 * se_rt       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Reaction Time Using 'trials' ------------------------------------
m_string_rt <- "Reaction Time (sec)"  # Label for y-axis
plot_title_rt <- glue('Reaction Times Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_rt, aes(x = trials, y = mean_rt, fill = session_cond)) +
  
  # Plot bars representing mean reaction times for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_rt, ymax = upper_ci_rt), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_rt, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_rt,
       x = "Trials",
       y = m_string_rt) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the reaction time plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/WQ1_rt_bars_test1.png', bg = 'white')
```


```{r}
# WQ1 Accuracy plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_acc <- complete_WQ1 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_acc <- df_acc %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_acc = mean(acc, na.rm = TRUE),
    se_acc = sd(acc, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_acc = mean_acc - 1.96 * se_acc,      # Lower bound of 95% CI
    upper_ci_acc = mean_acc + 1.96 * se_acc       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Accuracy Using 'trials' ------------------------------------
m_string_acc <- "Accuracy"  # Label for y-axis
plot_title_acc <- glue('Accuracy Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_acc, aes(x = trials, y = mean_acc, fill = session_cond)) +
  
  # Plot bars representing mean Accuracy for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_acc, ymax = upper_ci_acc), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_acc, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_acc,
       x = "Trials",
       y = m_string_acc) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the Accuracy plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/WQ1_acc_bars_test1.png', bg = 'white')
```


# (BQ1) Response and Reaction Time: "How strongly did you feel your body?"
```{r}
# BQ1 Reaction-times plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_rt <- complete_BQ1 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_rt <- df_rt %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    se_rt = sd(rt, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_rt = mean_rt - 1.96 * se_rt,      # Lower bound of 95% CI
    upper_ci_rt = mean_rt + 1.96 * se_rt       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Reaction Time Using 'trials' ------------------------------------
m_string_rt <- "Reaction Time (sec)"  # Label for y-axis
plot_title_rt <- glue('Reaction Times Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_rt, aes(x = trials, y = mean_rt, fill = session_cond)) +
  
  # Plot bars representing mean reaction times for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_rt, ymax = upper_ci_rt), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_rt, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_rt,
       x = "Trials",
       y = m_string_rt) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the reaction time plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/BQ1_rt_bars_test1.png', bg = 'white')
```
```{r}

# BQ1 Responses plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_resp <- complete_BQ1 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_resp <- df_resp %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_resp = mean(resp, na.rm = TRUE),
    se_resp = sd(resp, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_resp = mean_resp - 1.96 * se_resp,      # Lower bound of 95% CI
    upper_ci_resp = mean_resp + 1.96 * se_resp       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Responses Using 'trials' ------------------------------------
m_string_resp <- "Response (scale from 1 to 4)"  # Label for y-axis
plot_title_resp <- glue('Responses Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_resp, aes(x = trials, y = mean_resp, fill = session_cond)) +
  
  # Plot bars representing mean responses for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_resp, ymax = upper_ci_resp), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_resp, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_resp,
       x = "Trials",
       y = m_string_resp) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(breaks = 0:4) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the reaction time plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/BQ1_resp_bars_test1.png', bg = 'white')
```


# (WQ2) Response and Reaction Time: "How difficult was it to count how many times the word was mirrored?"
```{r}
# WQ2 Reaction-times plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_rt <- complete_WQ2 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_rt <- df_rt %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    se_rt = sd(rt, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_rt = mean_rt - 1.96 * se_rt,      # Lower bound of 95% CI
    upper_ci_rt = mean_rt + 1.96 * se_rt       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Reaction Time Using 'trials' ------------------------------------
m_string_rt <- "Reaction Time (sec)"  # Label for y-axis
plot_title_rt <- glue('Reaction Times Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_rt, aes(x = trials, y = mean_rt, fill = session_cond)) +
  
  # Plot bars representing mean reaction times for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_rt, ymax = upper_ci_rt), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_rt, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_rt,
       x = "Trials",
       y = m_string_rt) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the reaction time plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/WQ2_rt_bars_test1.png', bg = 'white')
```

```{r}

# WQ2 Responses plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_resp <- complete_WQ2 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_resp <- df_resp %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_resp = mean(resp, na.rm = TRUE),
    se_resp = sd(resp, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_resp = mean_resp - 1.96 * se_resp,      # Lower bound of 95% CI
    upper_ci_resp = mean_resp + 1.96 * se_resp       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Responses Using 'trials' ------------------------------------
m_string_resp <- "Response (scale from 1 to 4)"  # Label for y-axis
plot_title_resp <- glue('Responses Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_resp, aes(x = trials, y = mean_resp, fill = session_cond)) +
  
  # Plot bars representing mean responses for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_resp, ymax = upper_ci_resp), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_resp, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_resp,
       x = "Trials",
       y = m_string_resp) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(breaks = 0:4) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the reaction time plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/WQ2_resp_bars_test1.png', bg = 'white')
```


# (BQ2) Response and Reaction Time: "How difficult was it to feel your body?"
```{r}
# BQ2 Reaction-times plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_rt <- complete_BQ2 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_rt <- df_rt %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    se_rt = sd(rt, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_rt = mean_rt - 1.96 * se_rt,      # Lower bound of 95% CI
    upper_ci_rt = mean_rt + 1.96 * se_rt       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Reaction Time Using 'trials' ------------------------------------
m_string_rt <- "Reaction Time (sec)"  # Label for y-axis
plot_title_rt <- glue('Reaction Times Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_rt, aes(x = trials, y = mean_rt, fill = session_cond)) +
  
  # Plot bars representing mean reaction times for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_rt, ymax = upper_ci_rt), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_rt, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_rt,
       x = "Trials",
       y = m_string_rt) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the reaction time plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/BQ2_rt_bars_test1.png', bg = 'white')
```


```{r}

# BQ2 Responses plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_resp <- complete_BQ2 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_resp <- df_resp %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_resp = mean(resp, na.rm = TRUE),
    se_resp = sd(resp, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_resp = mean_resp - 1.96 * se_resp,      # Lower bound of 95% CI
    upper_ci_resp = mean_resp + 1.96 * se_resp       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Responses Using 'trials' ------------------------------------
m_string_resp <- "Response (scale from 1 to 4)"  # Label for y-axis
plot_title_resp <- glue('Responses Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_resp, aes(x = trials, y = mean_resp, fill = session_cond)) +
  
  # Plot bars representing mean responses for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_resp, ymax = upper_ci_resp), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_resp, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_resp,
       x = "Trials",
       y = m_string_resp) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(breaks = 0:4) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the reaction time plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/BQ2_resp_bars_test1.png', bg = 'white')
```