```
# Liisbeth's code for LPS study behavioral analysis

##### Edited by Holland Brown to plot effect of block (time) on behav scores

##### Updated 2024-09-30
##### Created 2024-09-09

## Notes:
#### Get timing info (block labels) from /LPS_STHLM/sourcedata/InteroceptionLogFiles/ses-0{1-4}_onsets.csv
#### BQ = body question (i.e. interoception); WQ = word question (i.e. exteroception)

```

#1. Packages
```{r}
library(dplyr)         #needed for filtering the data
library(ggplot2)       #needed for plotting the data
library(reshape2)      #needed for changing between long/wide format
library(readxl)        #needed for importing excel files
library(ggpubr)        #needed for adding significance bars to plots
library(car)           #for recoding the values

# Mixed effects linear models
library(lme4)
library(lmerTest)
library(emmeans) # post-hoc comparisons

# Other useful R packages
library(glue) # lets me code sort of like I can with f-strings in Python (sort of)
```

#2. Setting the working directory and importing behavioral data
```{r}
setwd("/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data") # location of data and this script
task_ses1 <- read.csv("summary_ses-01_interoception_responses.csv") # contains condition, reaction time, and response for one session
task_all_sessions <- read.csv("summary_allsessions_interoception_responses.csv") # contains condition, reaction time, and response for all sessions
task_all_sessions_acc <- read.csv("summary_allsessions_interoception_acc.csv") # contains condition, reaction time, response, and accuracy for all sessions
session_conditions <- read_excel("cond_ses_info.xlsx") # contains condition names ("morningpl", "morninglps", etc)
```

#3. Data preparation
```{r}

## 3.1. Merging the info from two datasets: Matching session number (e.g. "ses-01") to the condition (e.g. "plmorning")
session_long <- melt(session_conditions, id.vars = c("subjectID", "anat", "pls", "group"), value.name = "session_cond", variable.name = "session_num") # change session info file to long format

# Merge task_all_sessions, task_all_sessions_acc by matching subject ID, condition, reation time, session, and response
merged_all_sessions_acc <- left_join(task_all_sessions, task_all_sessions_acc, by=join_by(subjid == subjid, cond == cond, rt == rt, session == session, resp == resp), relationship = "many-to-one", multiple = "first")

# Merge the datasets based on matching subject IDs and session numbers in both datasets. Result is a merged dataset containing the session number and session condition
merged_all_sessions <- left_join(merged_all_sessions_acc, session_long, by=join_by(subjid == subjectID, session == session_num))


## 3.2. Recoding the labels (recode responses on the 4-point scale in the opposite direction)
merged_all_sessions$resp_re <- car::recode(merged_all_sessions$resp, "1 = 4; 2 = 3; 3 = 2; 4 = 1")
merged_all_sessions$cresp_re <- car::recode(merged_all_sessions$cresp, "1 = 4; 2 = 3; 3 = 2; 4 = 1")


## 3.3. Separating interoception and exteroception
### 3.3.1. Interoception: Separating BQ1 & BQ2
merged_inter <- data.frame(dplyr::filter(merged_all_sessions, merged_all_sessions$cond == "BQ1" | merged_all_sessions$cond == "BQ2"))
merged_interBQ1 <- data.frame(dplyr::filter(merged_all_sessions, merged_all_sessions$cond == "BQ1"))
merged_interBQ2 <- data.frame(dplyr::filter(merged_all_sessions, merged_all_sessions$cond == "BQ2"))

####### Filtering for participants, who have data for all sessions
complete_BQ1 <- dplyr::filter(merged_interBQ1, merged_interBQ1$subjid != "sub-120" & merged_interBQ1$subjid != "sub-138" & merged_interBQ1$subjid != "sub-141")
complete_BQ2 <- dplyr::filter(merged_interBQ2, merged_interBQ1$subjid != "sub-120" & merged_interBQ1$subjid != "sub-138" & merged_interBQ1$subjid != "sub-141")

### 3.3.1. Exteroception: Separating WQ1 & WQ2
merged_exte <- data.frame(dplyr::filter(merged_all_sessions, merged_all_sessions$cond == "WQ1" | merged_all_sessions$cond == "WQ2"))
merged_exteWQ1 <- data.frame(dplyr::filter(merged_all_sessions, merged_all_sessions$cond == "WQ1"))
merged_exteWQ2 <- data.frame(dplyr::filter(merged_all_sessions, merged_all_sessions$cond == "WQ2"))

####### Filtering for participants, who have data for all sessions
complete_WQ1 <- dplyr::filter(merged_exteWQ1, merged_exteWQ1$subjid != "sub-120" & merged_exteWQ1$subjid != "sub-138" & merged_exteWQ1$subjid != "sub-141")
complete_WQ2 <- dplyr::filter(merged_exteWQ2, merged_exteWQ1$subjid != "sub-120" & merged_exteWQ1$subjid != "sub-138" & merged_exteWQ1$subjid != "sub-141")


```


#4. Mixed effects linear models

##4.1 Effect of block on response with condition as a fixed effect and subject as a random effect
```{r}
# df <- merged_exte # exteroception
df <- merged_inter # interoception

# Fit the model
model <- lmer(resp ~ block * session_cond + (1 | subjid), data = df)

# Summary of the model
summary(model)

# Check residuals
# plot(model)

# Perform ANOVA to check significance of terms
anova(model)


```

##4.2 Effect of block on reaction time with condition as a fixed effect and subject as a random effect
```{r}
# df <- merged_exte # exteroception
df <- merged_inter # interoception

# Fit the model
model <- lmer(rt ~ block * session_cond + (1 | subjid), data = df)

# Summary of the model
summary(model)

# Check residuals
# plot(model)

# Perform ANOVA to check significance of terms
anova(model)

# Post-hoc comparisons
emmeans(model, pairwise ~ block * session_cond)

```


##4.5 Difference in block effects across conditions and extero/intero
```{r}
df <- merged_all_sessions # interoception and exteroception

# Modify the model to focus on block and condition interaction
model_block_condition <- lmer(rt ~ block * session_cond + (1 | subjid), data = df)

# # Summary of the model
# summary(model_block_condition)

# # Post-hoc comparisons: contrast block effects across conditions
# emm <- emmeans(model_block_condition, ~ block | session_cond, pbkrtest.limit = 3843)
# 
# # Pairwise comparison of block effects across conditions
# pairs(emm)

# run ANOVA on model to see significance of the residuals
anova(model_block_condition)

# Plot block effects across conditions
ggplot(df, aes(x = block, y = rt, color = session_cond)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ session_cond) +
  theme_minimal() +
  labs(title = "Effect of Block on Accuracy Across Conditions",
       x = "Block",
       y = "Accuracy")



```



##4.6 Difference in block effects in conditions separately
```{r}
# NOTE: in prev. model, found that block effect depends on condition, so modeling them here separately

# Conditions (session_cond)
condition <- 'lps'
# condition <- 'pl'
# condition <- 'morninglps'
# condition <- 'morningpl'

df_allconds <- merged_all_sessions # interoception and exteroception
df <- data.frame(dplyr::filter(df_allconds, df_allconds$session_cond == condition))

# Modify the model to focus on block and condition interaction
model <- lmer(rt ~ block + (1 | subjid), data = df)

# Summary of the model
summary(model_block_condition)

# # Post-hoc comparisons: contrast block effects across conditions
# emm <- emmeans(model_block_condition, ~ block | session_cond, pbkrtest.limit = 3843)
# 
# # Pairwise comparison of block effects across conditions
# pairs(emm)

# run ANOVA on model to see significance of the residuals
anova(model)

```

#4.6.1 Plot subjects' trajectories over time for all conditions
```
Measures to Plot:
  - reaction time (rt)
  - accuracy (acc)
  - response (resp)
  
Don't Plot
  - response reverse-coded (resp_re)
  - correct response reverse-coded (cresp_re)
  
NOTES:
  - BQ1: How strong did you feel your body?
  - BQ2: How difficult was it to focus on your body?
  - WQ1: How many times was the word mirrored? >> only question to which accuracy applies
  - WQ2: How difficult was it to count the times the word was mirrored?


  
```
```{r}
merged_BQ2_WQ2 <- rbind(complete_BQ2, complete_WQ2) # merge and save


df <- merged_BQ2_WQ2 # this will be overwritten if you rerun this for different questions
# measure <- resp # measure you want to plot (resp, cresp, rt, acc)
m_string <- "Response (Higher = more difficult)" # string describing the measure for plot titles and labels

plot_title <- glue('Task (Intero- and Exteroception) Difficulty Over Blocks')

# # Create a plot with each subject's trajectory across blocks, faceted by condition
# ggplot(df, aes(x = block, y = rt, group = subjid, color = subjid)) +
#   geom_line() +  # plot a line for each subject
#   geom_point() +  # add points at each block for each subject
#   facet_wrap(~ session_cond) +  # create a separate panel for each condition
#   theme_minimal() +  # use a minimal theme
#   labs(title = "Subject Accuracy Over Blocks Across Conditions",
#        x = "Block",
#        y = "Accuracy") +
#   theme(legend.position = "none")  # hide legend

# Calculate average measure for each block and condition
# TRY PLOTTING STDD -> see if ppl's perception of difficulty changes in a pattern
avg_data <- df %>%
  group_by(session_cond, block) %>%
  summarise(avg = sd(resp, na.rm=TRUE)) # add param to ignore NaNs
  # summarise(avg = mean(resp, na.rm=TRUE)) # add param to ignore NaNs

# Plot subject trajectories and average lines
ggplot() +
  # Plot individual subject trajectories with transparency
  geom_line(data = df, aes(x = block, y = resp, group = subjid, 
            color = subjid), alpha = 0.3) +  # make subject lines more transparent (modulate alpha)
  
  # Plot points for subject data (may remove later)
  geom_point(data = df, aes(x = block, y = resp, group = subjid,
             color = subjid), alpha = 0.3) +   # make subject points more transparent
  
  # Plot average trajectory for each condition in black
  geom_line(data = avg_data, aes(x = block, y = avg), color = "black", size = .75) +  # black average line
  geom_point(data = avg_data, aes(x = block, y = avg), color = "black", size = 1) +  # points on average line
  
  # Facet by condition (in R, a 'facet' is a figure panel)
  facet_wrap(~ session_cond) +
  
  # Labels and theme
  theme_minimal() +
  labs(title = plot_title,
       x = "Block",
       y = m_string) +
  theme(legend.position = "none")  # No legend for subjects

ggsave <- function(..., bg = 'white') ggplot2::ggsave(..., bg = bg)
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/BQ2_WQ2_resp_change_sd.png')

```

# (BQ2 and WQ2) Combined Intero- and Exteroception Difficulty Scores
```{r}
# Mean Bars
# Error Bars: mean ± 1.96 * (SE)

# Merge datasets
merged_BQ2_WQ2 <- rbind(complete_BQ2, complete_WQ2)

# Assign merged data to df
df <- merged_BQ2_WQ2
m_string <- "Response (Higher = more difficult)"  # String for plot labels

# Title for the plot
plot_title <- glue('Task (Intero- and Exteroception) Difficulty Over Blocks')

# Summarize data to calculate median, SE, and 95% confidence intervals
summary_data <- df %>%
  group_by(session_cond, block) %>%
  summarise(
    mean_resp = mean(resp, na.rm = TRUE),
    se_resp = sd(resp, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci = mean_resp - 1.96 * se_resp,       # Lower bound of 95% CI
    upper_ci = mean_resp + 1.96 * se_resp        # Upper bound of 95% CI
  )

# Create a bar plot with error bars for 95% confidence intervals
ggplot(summary_data, aes(x = factor(block), y = mean_resp, fill = session_cond)) +
  # Plot bars representing medians
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, position = position_dodge(0.9)) +
  
  # Facet by condition
  facet_wrap(~ session_cond) +
  
  # Labels and theme
  labs(title = plot_title,
       x = "Block",
       y = m_string) +
  theme_minimal() +
  theme(legend.position = "none")  # No legend for blocks

# Save the plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/BQ2_WQ2_resp_bar_mean_CI.png', bg = 'white')


```

# (WQ1) Accuracy and Reaction Time: "How many times was the word mirrored?"
```{r}
# WQ1 Reaction-times plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_rt <- complete_WQ1 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_rt <- df_rt %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    se_rt = sd(rt, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_rt = mean_rt - 1.96 * se_rt,      # Lower bound of 95% CI
    upper_ci_rt = mean_rt + 1.96 * se_rt       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Reaction Time Using 'trials' ------------------------------------
m_string_rt <- "Reaction Time (sec)"  # Label for y-axis
plot_title_rt <- glue('Reaction Times Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_rt, aes(x = trials, y = mean_rt, fill = session_cond)) +
  
  # Plot bars representing mean reaction times for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_rt, ymax = upper_ci_rt), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_rt, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_rt,
       x = "Trials",
       y = m_string_rt) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the reaction time plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/WQ1_rt_bars_test1.png', bg = 'white')
```


```{r}
# WQ1 Accuracy plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_acc <- complete_WQ1 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_acc <- df_acc %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_acc = mean(acc, na.rm = TRUE),
    se_acc = sd(acc, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_acc = mean_acc - 1.96 * se_acc,      # Lower bound of 95% CI
    upper_ci_acc = mean_acc + 1.96 * se_acc       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Accuracy Using 'trials' ------------------------------------
m_string_acc <- "Accuracy"  # Label for y-axis
plot_title_acc <- glue('Accuracy Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_acc, aes(x = trials, y = mean_acc, fill = session_cond)) +
  
  # Plot bars representing mean Accuracy for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_acc, ymax = upper_ci_acc), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_acc, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_acc,
       x = "Trials",
       y = m_string_acc) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the Accuracy plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/WQ1_acc_bars_test1.png', bg = 'white')
```


# (BQ1) Response and Reaction Time: "How strongly did you feel your body?"
```{r}
# BQ1 Reaction-times plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_rt <- complete_BQ1 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_rt <- df_rt %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    se_rt = sd(rt, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_rt = mean_rt - 1.96 * se_rt,      # Lower bound of 95% CI
    upper_ci_rt = mean_rt + 1.96 * se_rt       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Reaction Time Using 'trials' ------------------------------------
m_string_rt <- "Reaction Time (sec)"  # Label for y-axis
plot_title_rt <- glue('Reaction Times Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_rt, aes(x = trials, y = mean_rt, fill = session_cond)) +
  
  # Plot bars representing mean reaction times for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_rt, ymax = upper_ci_rt), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_rt, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_rt,
       x = "Trials",
       y = m_string_rt) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the reaction time plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/BQ1_rt_bars_test1.png', bg = 'white')
```
```{r}

# BQ1 Responses plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_resp <- complete_BQ1 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_resp <- df_resp %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_resp = mean(resp, na.rm = TRUE),
    se_resp = sd(resp, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_resp = mean_resp - 1.96 * se_resp,      # Lower bound of 95% CI
    upper_ci_resp = mean_resp + 1.96 * se_resp       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Responses Using 'trials' ------------------------------------
m_string_resp <- "Response (scale from 1 to 4)"  # Label for y-axis
plot_title_resp <- glue('Responses Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_resp, aes(x = trials, y = mean_resp, fill = session_cond)) +
  
  # Plot bars representing mean responses for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_resp, ymax = upper_ci_resp), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_resp, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_resp,
       x = "Trials",
       y = m_string_resp) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(breaks = 0:4) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the reaction time plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/BQ1_resp_bars_test1.png', bg = 'white')
```


# (WQ2) Response and Reaction Time: "How difficult was it to count how many times the word was mirrored?"
```{r}
# WQ2 Reaction-times plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_rt <- complete_WQ2 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_rt <- df_rt %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    se_rt = sd(rt, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_rt = mean_rt - 1.96 * se_rt,      # Lower bound of 95% CI
    upper_ci_rt = mean_rt + 1.96 * se_rt       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Reaction Time Using 'trials' ------------------------------------
m_string_rt <- "Reaction Time (sec)"  # Label for y-axis
plot_title_rt <- glue('Reaction Times Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_rt, aes(x = trials, y = mean_rt, fill = session_cond)) +
  
  # Plot bars representing mean reaction times for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_rt, ymax = upper_ci_rt), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_rt, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_rt,
       x = "Trials",
       y = m_string_rt) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the reaction time plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/WQ2_rt_bars_test1.png', bg = 'white')
```

```{r}

# WQ2 Responses plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_resp <- complete_WQ2 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_resp <- df_resp %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_resp = mean(resp, na.rm = TRUE),
    se_resp = sd(resp, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_resp = mean_resp - 1.96 * se_resp,      # Lower bound of 95% CI
    upper_ci_resp = mean_resp + 1.96 * se_resp       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Responses Using 'trials' ------------------------------------
m_string_resp <- "Response (scale from 1 to 4)"  # Label for y-axis
plot_title_resp <- glue('Responses Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_resp, aes(x = trials, y = mean_resp, fill = session_cond)) +
  
  # Plot bars representing mean responses for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_resp, ymax = upper_ci_resp), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_resp, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_resp,
       x = "Trials",
       y = m_string_resp) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(breaks = 0:4) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the reaction time plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/WQ2_resp_bars_test1.png', bg = 'white')
```


# (BQ2) Response and Reaction Time: "How difficult was it to feel your body?"
```{r}
# BQ2 Reaction-times plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_rt <- complete_BQ2 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_rt <- df_rt %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_rt = mean(rt, na.rm = TRUE),
    se_rt = sd(rt, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_rt = mean_rt - 1.96 * se_rt,      # Lower bound of 95% CI
    upper_ci_rt = mean_rt + 1.96 * se_rt       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Reaction Time Using 'trials' ------------------------------------
m_string_rt <- "Reaction Time (sec)"  # Label for y-axis
plot_title_rt <- glue('Reaction Times Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_rt, aes(x = trials, y = mean_rt, fill = session_cond)) +
  
  # Plot bars representing mean reaction times for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_rt, ymax = upper_ci_rt), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_rt, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_rt,
       x = "Trials",
       y = m_string_rt) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the reaction time plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/BQ2_rt_bars_test1.png', bg = 'white')
```


```{r}

# BQ2 Responses plot

# Step 1: Ensure Correct 'trials' Assignment -----------------------------------
df_resp <- complete_BQ2 %>%
  group_by(subjid, session_cond) %>%
  mutate(trials = row_number())  # Assign trial numbers from 1 to 10 for each participant and condition

# Step 2: Summarize Data by 'session_cond' and 'trials' -------------------------
summary_resp <- df_resp %>%
  group_by(session_cond, trials) %>%
  summarise(
    mean_resp = mean(resp, na.rm = TRUE),
    se_resp = sd(resp, na.rm = TRUE) / sqrt(n()),  # Standard error
    lower_ci_resp = mean_resp - 1.96 * se_resp,      # Lower bound of 95% CI
    upper_ci_resp = mean_resp + 1.96 * se_resp       # Upper bound of 95% CI
  ) %>%
  ungroup()  # Ensure no unwanted groupings

# Step 3: Plot Responses Using 'trials' ------------------------------------
m_string_resp <- "Response (scale from 1 to 4)"  # Label for y-axis
plot_title_resp <- glue('Responses Over Trials')  # Title for the plot

# Create the bar plot
ggplot(summary_resp, aes(x = trials, y = mean_resp, fill = session_cond)) +
  
  # Plot bars representing mean responses for each trial
  geom_col(position = "dodge", alpha = 0.7) +
  
  # Add error bars for 95% confidence intervals
  geom_errorbar(aes(ymin = lower_ci_resp, ymax = upper_ci_resp), width = 0.2, position = position_dodge(0.9)) +
  
  # Add a red line connecting the mean values of each trial
  geom_line(aes(x = trials, y = mean_resp, group = session_cond), color = "red", size = 1) +
  
  # Facet the plot by condition, so each condition has its own panel
  facet_wrap(~ session_cond) +
  
  # Labels and theme adjustments
  labs(title = plot_title_resp,
       x = "Trials",
       y = m_string_resp) +
  
  # Ensure x-axis reflects trials from 1 to 10 without clustering
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(breaks = 0:4) +
  
  theme_minimal() +
  theme(legend.position = "none")  # No legend for conditions

# Save the reaction time plot
ggsave('/home/common/piaf/LPS_STHLM/analysis_2023/LPS_behavioral_data/block_effects_results/BQ2_resp_bars_test1.png', bg = 'white')
```